### 2018-03-02 Paper/jaccardbaetica.tex
add new changes
modify introduction

All the amphora stamps belong to Dressel 20 types \citep{martin-kilcher_romischen_1994}. Dressel 20 was used to transport olive oil along the province during the Roman Empire \citep{berni_millet_epigrafianforica_2008}. Most Dressel 20 were marked in stamps and tituli picti and inked in graffities with different information but there is not a general consensus about the meaning of them \citep{rodriguez_baetican_1998}. Stamps are the most studied in this type of amphorae. There is evidence that stamps were used from three centuries. (economía oleica betica). Frequently, stamps were marked mainly in handles but rarely in rims and body.

@@

The meaning of the amphora stamps is still under debate. Some authors suggest that they were identified as the land-owners of the olive groves \citep{rodriguez_economioleicola_1977}. Other authors propose that stamp could be the owners of the making-amphorae workshop. In any case, the use of these stamps defined somehow the system of working in the workshops. 
%habría que citar a Dressel
%olive producing

@@

The analysis shows that amphoric stamps are not correlated with spatial distance. A matrix distance of similarity between workshops can be seen in Fig.1. The matrix displays

>>>>

All the amphora stamps belong to Dressel 20 types \citep{martin-kilcher_romischen_1994}. Dressel 20 is commonly associated with transportation of Baetican olive oil through the provinces during the Roman Empire \citep{berni_millet_epigrafianforica_2008}. Most Dressel 20 were marked in stamps and \textit{tituli picti} and inked in graffities with different information but there is not a general consensus about the meaning of them \citep{rodriguez_baetican_1998}. Stamps are the most studied in this type of amphorae. There is evidence that stamps were used for almost three centuries. (economía oleica betica). Frequently, stamps were marked mainly in handles but rarely in rims and body.

@@

The meaning of the amphora stamps is still under debate. Some authors suggest that they were identified as the land-owners of the olive groves \citep{rodriguez_economioleicola_1977}. Other authors propose that stamp could be the owners of the making-amphorae workshop (CITAR) or even a production counting system \citep{berni_millet_epigrafianforica_2008}. In any case, the use of these stamps defined somehow the system of working in the workshops. 
%habría que citar a Dressel
%olive producing

@@

The analysis shows that amphoric stamps are not correlated with spatial distance.

A matrix distance of similarity between workshops can be seen in Fig.1. The matrix displays
